Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-20 paper/ms.tex
Update observational section with lenticular gal

@@

{\bf Finally, we mention the evolution of \Rot{} in our simulation. In the
$N$-body simulation, the bar forms with $\Rot\sim1.6$ at $t=0\,\textrm{Gyr}$,
which is already well within the slow bar regime. After $5\,\textrm{Gyr}$ of
evolution, \Rot{} has risen to $\sim1.9$. In the SMUGGLE simulation, the gas is
added to the $t=0\,\textrm{Gyr}$ snapshot, so it begins with $\Rot{}\sim1.6$. As
expected, after $5\,\textrm{Gyr}$ of evolution \Rot{} is still $\sim1.6$.
However, this relies on our measure of the bar length as being the maximum
radius of all orbits trapped in the bar, which is not an observationally
accessible measure of bar length. One would need to test different
observationally possible bar length estimators, such as ellipse fitting
\citep{1990MNRAS.245..130A, 1999AAS..140....1M, 2002MNRAS.330...35A,
2006AA...452...97M, 2009AA...495..491A, 2015AA...576A.102A}. This is beyond the
scope of our current work. Nonetheless, our prediction that \Rot{} is stable in
the presence of gas is robust. Why the $N$-body simulation forms a bar with
$\Rot\sim1.6$ is a separate question deserving further attention.}

>>>>

{\bf Lenticular galaxies which lack a signficant gas phase offer an opportunity
to find slowly rotating bars. It would still take several Gyr for a galaxy
hosting a fast bar to transition to the slow bar regime, so slow bars should
only occupy lenticular galaxies which have been lenticular for some time.
NGC~4277 is one such example, whose bar has been found to rotate with
$\Rot{}\sim1.8$ \citep{2022AA...664L..10B}. On the other hand, NGC~4264 has a
fast bar with $\Rot{}\sim1$ \citep{2019MNRAS.488.4972C}. The difference has been
explained by differences in the dark matter content of the galaxies
\citep{2023MNRAS.521.2227B}. We offer another explanation based on the timing of
when gas was stripped from these galaxies.}

@@

{\bf Finally, we mention the evolution of \Rot{} in our simulation. In the
$N$-body simulation, the bar forms with $\Rot\sim1.6$ at $t=0\,\textrm{Gyr}$,
which is already well within the slow bar regime. After $5\,\textrm{Gyr}$ of
evolution, \Rot{} has risen to $\sim1.9$. In the SMUGGLE simulation, the gas is
added to the $t=0\,\textrm{Gyr}$ snapshot, so it begins with $\Rot{}\sim1.6$. As
expected, after $5\,\textrm{Gyr}$ of evolution \Rot{} is still $\sim1.6$.
However, this relies on our measure of the bar length as being the maximum
radius of all orbits trapped in the bar, which is not an observationally
accessible measure of bar length. One would need to test different
observationally possible bar length estimators, such as ellipse fitting
\citep{1990MNRAS.245..130A, 1999AAS..140....1M, 2002MNRAS.330...35A,
2006AA...452...97M, 2009AA...495..491A, 2015AA...576A.102A}. This is beyond the
scope of our current work. Nonetheless, our prediction that \Rot{} is stable in
the presence of gas is robust. Assuming bars form with $\Rot\sim1$, we predict
this should remain the case with further evolution. Why the $N$-body simulation
forms a bar with $\Rot\sim1.6$ is a separate question deserving further
attention.}
